\section{Awards}
\resumeItemListStart
    \resumeItem{\textbf{Representative ICT RnD Projects} in Recent Five Years (ICT RnD 사업 성과 중 우수과제), IITP (정보통신기획평가원), Republic of Korea, May 2022}
    \resumeItem{\textbf{CSE Young Scholar}, POSTECH Computer Science Engineering Department, Apr. 2022}
    \resumeItem{\textbf{Google Cloud Platform Credit Award}, Google LLC, USA, March 2022}
    \resumeItem{\textbf{28th HumanTech Paper Award (Silver Prize)}, Samsung Electronics Corp., Feb. 2022}
    \resumeItem{\textbf{Best EduTech Class Award}, POSTECH, \emph{Awarded to the one online class among 480 classes}, Nov. 2021}
    \resumeItem{\textbf{Representative Research Achievements}, POSTECH, July 2021}
    \resumeItem{\textbf{Qualcomm Gift Grant}, Qualcomm Corporation, Dec. 2020}
    \resumeItem{\textbf{The 16th Samsung EM Paper Contest (Silver Prize)}, Samsung Electro-Mechanics, Dec. 2020}
    \resumeItem{\textbf{Outstanding Online Class}, Awarded to five classes among 170 classes, POSTECH, July 2020}
    \resumeItem{\textbf{Faculty Support Program}, Intel Corporation, June 2020}
    \resumeItem{\textbf{Google Season of Docs}, Google Corporation, \emph{Technical writer support for Open3D}, Apr. 2019}
    \resumeItem{\textbf{Qualcomm Gift Grant}, Qualcomm Corporation, Sep. 2019}
    \resumeItem{Research Velocity Challenge Award, Intel Corporation, Dec. 2018}
    \resumeItem{Depth Estimation Challenge: Robustness Champion, CVPR workshop on Light Fields for Comp. Vis., July 2017}
    \resumeItem{\textbf{Qualcomm Innovation Award}, Qualcomm Korea Corp., March 2016}
    \resumeItem{CVPR 2015 Doctoral Consortium, IEEE CVPR, Apr. 2016}
    \resumeItem{\textbf{Honor Prize}, KAIST, \emph{Annual Ph.D. Research Progress Evaluation}, May 2016}
    \resumeItem{Best Paper Award, Korea Multimedia Society, \emph{2015 Spring Annual Conference}, May 2016}
    \resumeItem{\textbf{Honor Prize}, KAIST, \emph{Annual Ph.D. Research Progress Evaluation}, May 2015}
    \resumeItem{\textbf{20th HumanTech Paper Award (Silver Prize)}, Samsung Electronics Corp., Feb. 2014}
    \resumeItem{\textbf{19th HumanTech Paper Award (Silver Prize)}, Samsung Electronics Corp., Feb. 2013}
    \resumeItem{Best Paper Award, 25th Workshop on Image Processing and Image Understanding (IPIU2013), Feb. 2013}
    \resumeItem{Bronze Prize, Samsung Techwin research center conference, Feb. 2012}
    \resumeItem{Excellent Intern Award, Microsoft Research Asia, Dec. 2012}
    \resumeItem{\textbf{Microsoft Research Asia Fellowship}, Microsoft, \emph{Awarded to 11 Ph.D. students in the top Asian universities.}, Nov. 2011}
    \resumeItem{\textbf{Summa Cum Laude}, Hanyang University, \emph{GPA 4.32/4.5}, Feb. 2009}
    \resumeItem{\textbf{Full Scholarship}, Jeong-Su Scholarship Foundation, Aug. 2006}
    \resumeItem{\textbf{Scholarship for Undergraduate Students}, The Korea Foundation for Advanced Studies (KFAS), June 2006}
    \resumeItem{\textbf{Full scholarship}, Hanyang University, Aug. 2005}
\resumeItemListEnd



