\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{kotex}
\usepackage{enumitem}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\lfoot{Last modified: \today}
\cfoot{~~~~~~~~~~~~~~~~~~~~~~~\thepage\ of \pageref{LastPage}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \small{
  \item{#1 \vspace{-2pt}}
  }
}

\newcommand{\publicationItem}[4]{
  \small{
  \item{#1\\ \emph{#2}\\ #3\\ #4}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumePublicationListStart}{\begin{enumerate}[leftmargin=0.5in, label={[\arabic*]}]}
\newcommand{\resumePublicationListEnd}{\end{enumerate}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jaesik Park} \\ \vspace{3pt}
    \small \href{mailto:jaesik.park@postech.ac.kr}{\underline{jaesik.park@postech.ac.kr}} $|$ 
    \href{http://jaesik.info}{\underline{jaesik.info}}\\
    \footnotesize{Chungam-Ro 77, POSTECH, Pohang-Si, Republic of Korea (37673)}
\end{center}

\section{Working Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Assistant Professor}{Pohang, Republic of Korea}
      {Pohang University of Science and Technology \textnormal{(\textbf{POSTECH})}}{April. 2019 -- Present}
        \resumeItemListStart
          \resumeItem{Co-principal investigator of Computer Vision Lab.}
          \resumeItem{Advising about 20 masters and Ph.D. students}
          \resumeItem{Selected as one of the \textbf{POSTECH's Representative Research Achievements} (2021)}
          \resumeItem{Received \textbf{Outstanding Online Class award} (2020) and \textbf{the Best EduTech award} (2021)}
          \resumeItem{3D scene reconstruction, understanding, and assembly projects}
          \resumeItem{Proposed novel image generation pipelines: \textbf{StudioGAN} project (2.7k GitHub stars)}
          \resumeItem{5.1k Google Scholar citations}
        \resumeItemListEnd
    \resumeSubheading
      {Staff Research Scientist}{Santa Clara, CA, USA}
      {Intelligent Systems Lab, Intel (Manager: Dr. Vladlen Koltun)}{Dec. 2015 -- March 2019}
        \resumeItemListStart
          \resumeItem{\textbf{Co-founder of Open3D}: open-sourced 3D vision library, built from scratch (7.0k GitHub stars)}
          \resumeItem{Tanks and Temples: an online evaluation system for photogrametry methods}
          \resumeItem{High quality 3D reconstruction approaches}
          \resumeItem{Geometry understanding: tangent convolutions and fully convolutional geometric features}
          \resumeItem{Advised intern students from Stanford University, U.C. Berkeley, and Carnegie Melon University}
        \resumeItemListEnd
    \resumeSubheading
      {Post-Doc. Researcher}{Daejeon, Republic of Korea}
      {KAIST. Developed color correction algorithms (Mentor: Prof. In So Kweon)}{Aug. 2015 -- Nov. 2015}
    \resumeSubheading
      {Research Intern}{Redmond, WA, USA}
      {Microsoft Research. Developed a light calibration technique (Mentor: Dr. Sudipta N. Sinha)}{June 2013 -- Sep. 2013}
    \resumeSubheading
      {Research Intern}{Beijing, China}
      {Microsoft Research Asia. Multiview photometric stereo system (Mentor: Prof. Y. Matsushita)}{April 2012 -- Oct. 2012}     
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ph.D. and M.S. in Electrical Eng.}{Daejeon, Republic of Korea}
      {Korea Advanced Institute of Science and Technology \textnormal{(\textbf{KAIST})}}{Feb. 2009 -- Aug. 2015}
        \resumeItemListStart
        \resumeItem{Ph.D. thesis: Image-based 3D Modeling via Constrained Optimization (Advisor: Prof. In So Kweon, Co-advisor: Dr. Yu-Wing Tai)}
        \resumeItem{Master's thesis: Upsampling Low-resolution Image using Heterogeneous High-resolution Image (Advisor: Prof. In So Kweon)}
        \resumeItemListEnd
    \resumeSubheading
      {B.E. in Media Communication Eng.}{Seoul, Republic of Korea}
      {Hanyang University (\textbf{Summa cum laude})}{March. 2005 -- Feb. 2009}
  \resumeSubHeadingListEnd

  
