\section{Talks}
\resumeItemListStart
    \resumeItem{\textit{On overview of recent 3D vision methods}, Harvard University, Boston, MA, USA (online), June 2022}
    \resumeItem{\textit{Self-Calibrating Neural Radiance Fields}, Seoul National University, Seoul, Republic of Korea (online), Feb. 2022}
    \resumeItem{\textit{Self-Calibrating Neural Radiance Fields}, DGIST, Daegu, Republic of Korea, Aug. 2021}
    \resumeItem{\textit{Object Detection from Images or Point Clouds}, LG Electronics, Seoul, Republic of Korea, Aug. 2021}
    \resumeItem{\textit{Self-Calibrating Neural Radiance Fields}, Korea Institute of Science and Technology (KIST), Virtual, June 2021}
    \resumeItem{\textit{Mentor Session: How to Become a Professor}, Conference on Computer Vision and Pattern Recognition (CVPR 2021), Virtual, June 2021}
    \resumeItem{\textit{Recent Work on Image Generation}, Gwangju Institute of Science and Technology (GIST), Virtual, May 2021}
    \resumeItem{\textit{Point Cloud Registration using Hierachical Hough Transform}, 33rd Workshop on Image Processing and Image Understanding (IPIU2021), Virtual, Feb. 2021}
    \resumeItem{\textit{3D Representations and Detections}, Chungbuk University, Virtual, Jan. 2021}
    \resumeItem{\textit{Introduction to Computer Vision}, Kyungbuk Science High School, Pohang, Republic of Korea, Aug. 2020}
    \resumeItem{\textit{High-Dimensional Convolutional Networks for Geometric Pattern Recognition}, KCCV 2020, Seoul, Republic of Korea, Aug. 2020}
    \resumeItem{\textit{Object Detection from Images or Point Clouds}, LG Electronics, Seoul, Republic of Korea, Aug. 2020}
    \resumeItem{\textit{Geometric Pattern Recognition}, 32nd Workshop on Image Processing and Image Understanding (IPIU2020), Feb. 2020}
    \resumeItem{\textit{Fully Convolutional Geometric Features}, Koh Young Technology, Yongin, Republic of Korea, Dec. 2019}
    \resumeItem{\textit{Open3D Tutorial and Fully Convolutional Geometric Features}, Korea Electronics Technology Institute, Seongnam, Republic of Korea, Nov. 2019}
    \resumeItem{\textit{Introduction to Computer Vision and Deep Learning}, Daegu Science High School, Daegu, Republic of Korea, Aug. 2019}
    \resumeItem{\textit{3D Computer Vision and Open3D}, International Conference on Machine Vision Applications, Tokyo, Japan, May 2019}
    \resumeItem{\textit{3D Computer Vision and Open3D}, Qualcomm Head Quater, San Diego, USA, June 2019}
    \resumeItem{\textit{3D reconstruction using Open3D}, Minneapolis, University of Minnesota, invited lecture for Multiview 3D Geometry in Computer Vision (CSCI 5980) Class, Apr. 2018}
    \resumeItem{\textit{3D reconstruction using Open3D}, Forma Technology (a startup company at Bay Area), San Francisco, USA, March 2018}
\resumeItemListEnd



